User-customized hashtag/tag prediction on Twitter and StackOverflow:\protect \\ Comparing vector-based and ACT-R Bayesian models of tag retrieval

### 2013-10-06 writeups/proposal/proposal.tex
foo
Former-commit-id: bb734b37947a27134813331ead399a81c3b05171 [formerly 2df2d3ca55a21eec736d7e9ef461b4410f43c5f3]
Former-commit-id: 6d705b974bceb3abc79263708d5279a3c16542b1
foo
Former-commit-id: a9b6c08cae7c17671510e2b87bb1f6d4374f2e47 [formerly be0b1d3e61a374ee2c3e24b7b0b70f17883c4e87]
Former-commit-id: f572afdc6b45953edab071c76f43861b8aa0e270
foo
Former-commit-id: 2cfae7bd10bf1fd2598644a84faedbb84e6d8373 [formerly e32e5425aa8bb49b9725c16faa6d04bc5e1fb0a0]
Former-commit-id: f28e9b7304d115dc74c63c80df8af5796a40cebd

\usepackage[hyphens]{url}
%\usepackage{hyperref}
%\usepackage{breakurl}

\usepackage{subfigure}
\usepackage{graphicx}
\usepackage[group-separator={,}]{siunitx}
\RequirePackage[l2tabu, orthodox]{nag}
\graphicspath{{./figures/dissertation/}} % Specifies the directory where pictures are stored

@@

\title{User-customized hashtag/tag prediction on Twitter and StackOverflow:\protect \\ Comparing vector-based and ACT-R Bayesian models of tag retrieval}
%\shorttitle{Tag prediction on Twitter and StackOverflow}
\shorttitle{}

@@

@@

@@

\begin{figure}[!htbp]
  \scalebox{.9}{\resizebox{\linewidth}{!}{\includegraphics{superUserTagSuggestion.pdf}}}
  \caption{Example of tag suggestions when creating a post on the SuperUser site}
  \label{figSuperUserSuggestion}
\end{figure}

@@

\subsubsection{\textcite{Stanley2013}'s ACT-R DM Model for StackOverflow}

>>>>

\usepackage[hyphens]{url}

% ref: http://tex.stackexchange.com/questions/73862/how-can-i-make-a-clickable-table-of-contents
\usepackage{hyperref}
\hypersetup{
  colorlinks,
  citecolor=black,
  filecolor=black,
  linkcolor=black,
  urlcolor=black
}
%\hypersetup{linktocpage}

%\usepackage{breakurl}
\usepackage{subfigure}
\usepackage{graphicx}
\usepackage[group-separator={,}]{siunitx}
\RequirePackage[l2tabu, orthodox]{nag}
\graphicspath{{./figures/dissertation/}} % Specifies the directory where pictures are stored

@@

\title{User-customized hashtag/tag prediction on Twitter and StackOverflow:\protect \\ Comparing vector-based and ACT-R Bayesian models of tag retrieval}
\shorttitle{Tag prediction on Twitter and StackOverflow}
%\shorttitle{}

@@

\note{\today}

@@

\subsubsection{StackExchange}

@@

\begin{figure}[!htbp]
  \scalebox{.9}{\resizebox{\linewidth}{!}{\includegraphics{superUserTagSuggestion-crop.pdf}}}
  \caption{Example of tag suggestions when creating a post on the SuperUser site}
  \label{figSuperUserSuggestion}
\end{figure}

@@

% ref: http://tex.stackexchange.com/questions/53513/hyperref-token-not-allowed
\subsubsection{\texorpdfstring{\textcite{Stanley2013}}{Stanley2013}'s ACT-R DM Model for StackOverflow}
